---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

  ```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# pythonistr

[![travis_status](https://travis-ci.org/blmoore/pythonistr.svg?branch=master)](https://travis-ci.org/blmoore/pythonistr)
[![codecov](https://codecov.io/gh/blmoore/pythonistr/branch/master/graph/badge.svg)](https://codecov.io/gh/blmoore/pythonistr)
[![docs_badge](https://img.shields.io/badge/docs-latest-blue.svg)](http://blm.io/pythonistr)
[![CRAN_badge](http://www.r-pkg.org/badges/version/pythonistr)](https://cran.r-project.org/package=pythonistry)

pythonistr brings over a few ideas from the python language into R.

## Install

Install from github with:

```{r, eval = FALSE}
devtools::install_github("blmoore/pythonistr")
```

## Usage

```{r load_pkg, echo=FALSE}
library(pythonistr)
```

### Shortcuts

In python, to instantiate a list of strings with minimal typing you could use:

```{python}
print('i want a list of words'.split())
```

pythonistr adds `separate` (or `s` for short):

```{r}
s("saves you typing and matching quotes")
```

----------

String and sub-string matching intent is clear in Python:
```{python} 
if 'char' in 'character string':
   print('Found!')
```

pythonistr adds `%within%` as an alias for `grepl(pattern, string)`:

```{r}
if ('char' %within% 'character string')
  print('Found!')
```

------

### Python functions

Python has a great context management system that closes file connections
when they fall out of scope:

```{python with_example, eval=FALSE}
with open('file.csv', 'r') as f:
  for line in f:
    print(line)
```

Pythonistr adds a `with` method to connections which mirrors this behaviour:

```{r with_r, eval=FALSE}
file_conn <- file("file.csv", "r")
with(file_conn, {
  while (TRUE) {
    line <- readLines(file_conn, n = 1)
    if (length(line) == 0) {
      break
    }
    print(line)
  }
})

isOpen(file_conn) # FALSE (well, error)
```

Even better, there's some support for line-by-line processing. In Python you 
might write:

```{python iterate_stop, eval=FALSE}
with open('log.txt', 'r') as l:
  for line in l:
    print line
    if 'stop' in line:
      break
```

With pythonistr, you could write this as:

```{r iterate_stop_r, eval=FALSE}
log <- file('log.txt', 'r')
with(log,
  by_line(log, 
    print, # function to apply to each line
    function(l) grepl("stop", l) # stop when true
  )
)
```

Anything executed by `by_line` is currently only useful for its side-effects.


### Aliases

If you regularly switch between R and Python you might be used to 
getting tripped up by `length` vs. `len` but this isn't the only
example. For example: which language prefers `reversed` over `rev`? Which 
implements `sorted` as well as `sort`? 

pythonistr includes a few shortcuts to lower the context 
switching overhead, though it's probably a bad idea to rely 
on these in normal R programming.


