---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

  ```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# pythonistr

[![Travis-CI Build Status](https://travis-ci.org/blmoore/pythonistr.svg?branch=master)](https://travis-ci.org/blmoore/pythonistr)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/pythonistr)](https://cran.r-project.org/package=pythonistry)

pythonistr brings over a few ideas from the python language into R.

## Install

Install from github with:

```{r, eval = FALSE}
devtools::install_github("blmoore/pythonistr")
```

## Usage

```{r load_pkg, echo=FALSE}
library(pythonistr)
```

### Python functions

Python has a great context management system that closes file connections
when they fall out of scope:

```{python with_example, eval=FALSE}
with open('file.csv', 'r') as f:
  for line in f:
    print(line)
```

Pythonistr adds a `with` method to connections which mirrors this behaviour:

```{r with_r, eval=FALSE}
file_conn <- file("file.csv", "r")
with(file_conn, {
  while (length(line) != 0) {
    line <- readLines(file_conn, n = 1)
    print(line)
  }
})
```

### Aliases

If you regularly switch between R and Python you might be used to 
getting tripped up by `length` vs. `len` but this isn't the only
example.

Let's play Python or R:

* `rev` vs. `reversed`?
* `sort` or `sorted`?
